COVID-19 Closures Negatively Impact Restaurant Revenue and Employment

### 2021-02-22 outputs/paper/paper.Rmd

---
title: "COVID-19 Closures Negatively Impacts Restaurant Revenue and Employment"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "September 20th, 2021"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "A random controlled trial, with surveys, to identify the impact of mandatory partial closures on Ontario restaurants"
abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants. A randomized controlled trial was conducted and surveys were used to collect results. The data show that restaurant revenue and employee counts were negatively impacted by a mandatory two-week partial closure, and dine-in restaurants and restaurants owned by visible minorites were more negatively impacted. These results suggest that if more closures are necessary, Ontario should support restaurant owners by offering support for take-out services and minority-owned businesses."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

@@

# Appendix {-}

@@

# Appendix B {#appendixB}

TODO: ADD A SURVEY SCREENSHOT. REFERENCE IN THE MAIN PAPER.

@@

TODO: ADD A COMPLETE LIST OF SURVEY QUESTIONS AND OPTIONS. REFERENCE IN THE MAIN PAPER.

>>>>

---
title: "COVID-19 Closures Negatively Impact Restaurant Revenue and Employment"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "September 20th, 2021"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "A random controlled trial, with surveys, to identify the impact of mandatory partial closures on Ontario restaurants"
abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants. A randomized controlled trial was conducted and surveys were used to collect results. The data show that restaurant revenue and employee counts were negatively impacted by a mandatory two-week partial closure, and dine-in restaurants and restaurants owned by visible minorites were more negatively impacted. These results suggest that if more closures are necessary, Ontario should support restaurant owners by offering support for take-out services and minority-owned businesses."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

[Appendix B](#appendixB) contains screen captures of the online version of Survey 1 and Survey 2.
For images of the sheet included in the mailers for Survey 1 and Survey 2 sent to restaurant owners, containing all survey questions and answer options, refer to [Appendix C](#appendixC).

@@

@@

\newpage
# Appendix B {#appendixB}

```{r page1, echo=FALSE, fig.cap="Screen capture of the first section of Survey 1 and Survey 2.", out.width = '70%', fig.align="center"}
knitr::include_graphics(here("outputs/images/page1.png"))
```

```{r page2a, echo=FALSE, fig.cap="Screen capture of the second section of Survey 1.", out.width = '75%', fig.align="center"}
knitr::include_graphics(here("outputs/images/page2a.png"))
```

```{r page2b, echo=FALSE, fig.cap="Screen capture of the second section of Survey 2.", out.width = '75%', fig.align="center"}
knitr::include_graphics(here("outputs/images/page2b.png"))
```

```{r page3, echo=FALSE, fig.cap="Screen capture of the third section of Survey 1 and Survey 2.", out.width = '75%', fig.align="center"}
knitr::include_graphics(here("outputs/images/page3.png"))
```

```{r page4, echo=FALSE, fig.cap="Screen capture of the fourth section of Survey 1 and Survey 2.", out.width = '75%', fig.align="center"}
knitr::include_graphics(here("outputs/images/page4.png"))
```

\clearpage

@@

```{r survey1png, echo=FALSE, fig.cap="Image of the mailer sent to restaurant owners containing Survey 1.", out.width = '78%', fig.align="center"}
knitr::include_graphics(here("outputs/images/survey1.png"))
```
```{r survey2png, echo=FALSE, fig.cap="Image of the mailer sent to restaurant owners containing Survey 2.", out.width = '78%', fig.align="center"}
knitr::include_graphics(here("outputs/images/survey2.png"))
```
